---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  warning = FALSE
)
```

# kenyaweather

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/kenyaweather)](https://CRAN.R-project.org/package=kenyaweather)
[![R-CMD-check](https://github.com/merely-useful/kenyaweather/workflows/R-CMD-check/badge.svg)](https://github.com/merely-useful/kenyaweather/actions)
<!-- badges: end -->

The goal of kenyaweather is to ...

## Installation

You can install the released version of kenyaweather from [CRAN](https://CRAN.R-project.org) with:

``` r
remotes::install_github("merely-useful/kenyaweather")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(kenyaweather)

weather_report("Mombasa")
```

```{r}
weather_summary("Lodwar")
```

## Repository Structure

- `R/` contains the package functions.
- `dev-scripts/` contains a script to re-generate this repository.
> Don't run unless you want to overwrite things in the repo.

- `tests/` contains the tests.
- `.github/` is where both the community files such as `CONTRIBUTING.md` and the GitHub Actions live. 
