---
title: "example-report"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{example-report}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  warning = FALSE
)
```

```{r setup}
library(kenyaweather)
library(dplyr)
library(ggplot2)
```

The `kenyaweather` package includes two main functions to provide functionality around accessing weather data for different cities in Kenya. The first function is `weather_report` which generates visualizations of the 4 different variables available for a specified city. 

```{r}
weather_report("Mombasa")
```

The second function is the `weather_summary` function which generates a table that shows the year with maximum and minimum, the average across years and the standard deviation of the 4 different variables available for the specified city.

```{r}
weather_summary("Mombasa")
```

In addition to these two functions, the package also exports a data frame with the name `weather_data` which allows you to do further exploration and add further functionality such as in the following example:

```{r}
weather_data %>%
  filter(name == "MOMBASA") %>%
  ggplot(aes(x = tmin, y = tavg)) +
    geom_point(alpha = 0.10) +
    theme_minimal()
```
